\begin{center}
    \textbf{Acknowledgements}
\end{center}

The work presented here could not have been done without the help of many individuals in the WPI community. First and foremost, I would like to thank all the members of the WPI AiM lab. It was an honor to be a part of a group that is on the cutting edge of interventional medical robotics research. I am excited to see what this lab will achieve in the future and how it will benefit the field of medicine.

I am also very grateful for my wonderful committee member Prof. Karen Troy. Thank you for taking time out of your busy schedule to be a committee member for my project. I appreciate all the knowledge and expertise you brought to the table

Finally, I would like extend my gratitude to the three people who I could not have done this project without. Thank you Dr. Christopher Nycz for all the help you provided for me throughout my project and for being my committee member. From introducing me to the PracticePoint facilities to helping and teaching me the ins and outs of medical research, I could not have accomplished what I have done throughout my thesis.

Thank you Nathaniel Goldfarb for consistently being by my side throughout my thesis research as well as throughout your time as a teaching assistant. I have benefitted tremendously from the knowledge you have given me in several different fields.

Finally, thank you Prof. Gregory Fischer for advising me throughout my project. The motivation and passion you bring to our meetings inspires me and the other lab members in a way few professors have. I am honored to have had a year where I could learn from your wide area of expertise. I am excited to see the innovations you will help create in the future.

\newpage
\begin{center}
    \textbf{Dedication}
\end{center}

To all the teachers, professors, and mentors who have inspired and taught me throughout my life - my life accomplishments so far and in the future are all because of you. The fire in me to make and create came from the many sparks from you all.

To my parents, thank you for all you have done for me and my brother. The sacrifices, achievements, and passion you have both shown throughout our lives continue to inspire me to reach for the stars.