\chapter{Introduction}
Paraplegia is a medical term used to define where a patient loses feeling and/or movement in their lower two limbs. In comparison, quadriplegia (also sometimes known as tetraplegia) is the loss of control in all four limbs. Sudden walking disabilities, such as lower limb paralysis, change a person's mobility, and often have quite a significant effect on a person's lifestyle and health. Not all feeling/movement needs to be lost in order for someone to be considered paraplegic \cite{IncompleteTraumaticQuadrilegia}. Only 30\% of all paraplegic and quadriplegic patients are considered complete lesions, where there is no sensation and no mobility in the lower limbs \cite{RehabParaplegia}. Paraplegia can introduce a significant challenge to maintain healthy bone and muscle mass, as the patient usually will have a much harder time exercising. However, research has shown that controlled rehabilitation can actually help reconnect a patient's injured neurons, reducing the effects of the injury and regaining mobility and/or feeling in their lower limbs \cite{GaitTrainingClinical}. As such, a large part of a paralysis victim's life is devoted to rehabilitation and physical therapy.

Exercises for rehabilitation come in many forms, from stretching to strength training, to hydrotherapy. Gait training has specifically been shown to improve the quality of life of a lower-limb paralysis patient, but this exercise is very hard to do, especially with severe cases of paraplegia. Robotics and exoskeletons have been proposed and tested to help with this cause. A mechanical system with intelligent software control can be used to assist and hold a person's weight as they perform exercises as called for by their doctor. Such systems can decrease bone and muscle atrophy and help fight the side effects of paraplegia. Robotics and image processing have a very large opportunity to improve the rehabilitation process in paraplegic patients. Clinical research in using robotic orthoses for gait training and other rehabilitation exercises show positive improvement in most patients when considering quality of life \cite{GaitTrainingBenefitsRoboticsWalkbot} \cite{RoboticGaitTraining}. 

Most rehabilitation exoskeletons have placed their focus on the software control, and assumed joints like the hip, knee, and ankle to be pin joints. However, the knee joint specifically is known to not be a pin joint, as the shank linearly extends throughout flexion. This tibiofemoral relationship is often ignored, which may cause skin complications due to poor fitting when exoskeleton usage expands from just small clinical trials. This thesis aims to design and test a biomechanical actuated knee orthosis that can be customized to the natural tibiofemoral motion of a patient. It also aims to identify the tibiofemoral relationship in a person using modern imaging systems, such as motion capture systems and magnetic resonance imaging (MRI).

